---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE
)
```

# subsamplerr

<!-- badges: start -->

<!-- badges: end -->

R package for subsampling genomic data based on epidemiological time series data.

## Installation

You can install the development version of subsamplerr from GitHub with:

``` r
devtools::install_github("leke-lyu/subsamplerr")
```

```{r, echo=FALSE, warning=FALSE}

library(magrittr)
library(aweek)
library(ggplot2)
library(lubridate)
library(aweek)
library(tidyr)
library(dplyr)
```

## Example

Count the number of genome samples by Epi-Week and location, and Integrate daily count of case data into weekly count:

```{r, message = FALSE}
library(subsamplerr)

texasSeq <- texasSeqMeta %>% metaTableToMatrix(., "location", "date") %>% exactDateToEpiweek(.)
texasCase %<>% exactDateToEpiweek(.)
```

Inspect the sampling heterogeneity of the Texas dataset:

```{r dpi=600, fig.width = 10, fig.height= 6}
plotSequencingPercentage(texasSeq, texasCase)
```

Generate sampled dataset with baseline equals 0.006

```{r}
texasSample <- expectedSampleMatrix(0.006, texasSeq, texasCase)
id <- proportionalSampling(texasSample, texasSeqMeta)
```

Inspect the sampling heterogeneity of the sampled dataset:

```{r dpi=600, fig.width = 10, fig.height= 6}
plotSequencingPercentage(texasSample, texasCase)
```
