---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE
)
```

# subsamplerr

<!-- badges: start -->

<!-- badges: end -->

R package for subsampling genomic data based on epidemiological time series data.

## Installation

You can install the development version of subsamplerr from GitHub with:

``` r
devtools::install_github("leke-lyu/subsamplerr")
```

## Example

Inspect the genome metadata file:

```{r, message = FALSE}
library(subsamplerr)
head(texasSeqMeta)
```

Count the number of genome samples by week and location:

```{r}
library(magrittr)
library(aweek)
library(lubridate)
library(dplyr)

texasSeqMeta$epiweek <- paste0((texasSeqMeta$date %>% as.Date() %>% epiyear()), "_", (texasSeqMeta$date %>% as.Date() %>% epiweek()))
texasSeqCount <- texasSeqMeta %>%
  group_by(location, epiweek) %>% 
  summarise(total_count=n(), .groups = 'drop') %>%
  as.data.frame()
MetroAreas <- texasSeqCount$location %>% unique() %>% sort()
EpiweekS <- texasSeqCount$epiweek %>% unique() %>% sort()
texasSeq <- matrix(0, length(MetroAreas), length(EpiweekS))
rownames(texasSeq) <- MetroAreas
colnames(texasSeq) <- EpiweekS
for (i in 1:nrow(texasSeqCount)) {
  texasSeq[texasSeqCount[i, "location"] == MetroAreas, texasSeqCount[i, "epiweek"] == EpiweekS] <- texasSeqCount[i, "total_count"]
}
```

Integrate daily count of case data into weekly count:

```{r}
EpiweekC <- paste0((colnames(texasCase) %>% as.Date() %>% epiyear()), "_", (colnames(texasCase) %>% as.Date() %>% epiweek()))
colnames(texasCase) <- EpiweekC
texasCase <- t(rowsum(t(texasCase), colnames(texasCase)))
texasCase <- texasCase[rownames(texasSeq), colnames(texasSeq)]
```

Inspect the sampling heterogeneity of the Texas dataset:

```{r dpi=600, fig.width = 10, fig.height= 6}
plotSequencingPercentage(texasSeq, texasCase)
```

Generate sampled dataset with baseline equals 0.006

```{r}
texasSample <- expectedSampleMatrix(0.006, texasSeq, texasCase)
id <- proportionalSampling(texasSample, texasSeqMeta)
```

Inspect the sampling heterogeneity of the sampled dataset:

```{r dpi=600, fig.width = 10, fig.height= 6}
plotSequencingPercentage(texasSample, texasCase)
```
