---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE
)
```

# subsamplerr

<!-- badges: start -->

<!-- badges: end -->

Following the approach of [Anderson F. Brito](https://www.cell.com/cell/fulltext/S0092-8674(21)00434-7), we developed R scripts, later consolidated into an R package. This package processes case count tables and genome metadata, enabling visual exploration of sampling heterogeneity and the implementation of proportional sampling schemes.

## Installation

You can install the development version of subsamplerr from GitHub with:

``` r
devtools::install_github("leke-lyu/subsamplerr")
```

```{r, echo=FALSE, warning=FALSE}

library(magrittr)
library(aweek)
library(ggplot2)
library(lubridate)
library(aweek)
library(tidyr)
library(dplyr)
```

## Workflow Overview

### Input Data
- **texasSeqMeta**: Metadata of genome samples in Texas by location and date.
- **texasCase**: Daily case counts in Texas.

### Data Processing
- **metaTableToMatrix**: Converts `texasSeqMeta` into a matrix format by location and date.
- **dateToEpiweek**: Aggregates both genome and case data from daily counts to weekly counts.

### Heterogeneity Analysis
- **plotSequencingRatio**: Generates a visualization to inspect the sampling heterogeneity in the Texas dataset.

### Proportional Sampling
- **proposedSamplingMatrix**: Creates a sampling matrix based on a baseline ratio (0.006).
- **proportionalSampling**: Applies the sampling matrix to select a proportionate sample from `texasSeqMeta`.

### Post-sampling Heterogeneity Analysis
- **plotSequencingRatio**: Re-evaluates sampling heterogeneity in the sampled dataset for comparison with the original dataset.

## Example

```{r, message = FALSE}
library(subsamplerr)

texasSeq <- texasSeqMeta %>% metaTableToMatrix(., "location", "date") %>% dateToEpiweek(.)
texasCase %<>% dateToEpiweek(.)
```

```{r dpi=600, fig.width = 10, fig.height= 6}
plotSequencingRatio(texasSeq, texasCase)
```

```{r}
texasSample <- proposedSamplingMatrix(0.006, texasSeq, texasCase)
id <- proportionalSampling(texasSample, texasSeqMeta)
```

```{r dpi=600, fig.width = 10, fig.height= 6}
plotSequencingRatio(texasSample, texasCase)
```
